Reconstructing contact network parameters from viral phylogenies

### 2016-07-01 doc/figures/pipeline.tex
GLM thingies
Progress on paper changes

\begin{tikzpicture}
  [every node/.style={rectangle, draw, text width=4cm, align=center, rounded corners},
   every path/.style={->, >=stealth, thick}]
  \node (dl) {download sequences \\ from GenBank};
  \node (align) [below=of dl] {multiple sequence alignment with MUSCLE};
  \node (clip) [below=of align, dashed] {remove hypervariable regions};
  \node (tree) [right=of dl] {estimate unrooted phylogeny with FastTree2};
  \node (cluster) [below=of tree, dashed] {select cluster by patristic distance};
  \node (root) [below=of cluster] {root and scale phylogeny with root-to-tip regression};

>>>>

\begin{tikzpicture}
  [every node/.style={rectangle, draw, text width=4cm, align=center, rounded corners},
   every path/.style={->, >=stealth, thick},
   node distance=0.5 and 1]
  \node (dl) {download sequences \\ from GenBank};
  \node (align) [below=of dl] {multiple sequence alignment with MUSCLE};
  \node (clip) [below=of align, dashed] {remove hypervariable regions};
  \node (tree) [right=of dl] {estimate unrooted phylogeny with FastTree2};
  \node (cluster) [below=of tree, dashed] {select cluster (patristic distance) or subtree};
  \node (root) [below=of cluster] {root and scale phylogeny with root-to-tip regression};

### 2016-07-01 doc/ismb/poster.tex
Progress on paper changes

\addbibresource{papers.bib}
\setlength{\bibhang}{0pt}
\tikzposterlatexaffectionproofoff
\settitle{ \vbox{ \centering \color{titlefgcolor}
{\fontsize{2.5cm}{2cm}\selectfont \@title}
\\ --- \huge \@author~--- \\ \@institute } }

@@

% hacky things
\node [text width=6in] at ($ (current page.west) + (-0.42\paperwidth, -1.5in) $)
  { \LARGE ISMB \\ July 8-12, 2016 \\ Orlando, USA};
\node [text width=6in, align=right] at ($ (current page.west) + (0.42\paperwidth, -1.5in) $)
  { \LARGE rmccloskey@cfenet.ubc.ca \\ (604) 682-6344 ext. 63266 };

\begin{columns}
  \column{0.25}
  \block{Contact networks shape viral transmission trees}{
    \centerline{\includegraphics[width=0.2\textwidth]{contactnet}}
      Network structure can change the speed and pattern of epidemic spread,
      potentially informing public health interventions.
  }
  \block{}{\vspace{1cm}\color{blocktitlefgcolor}\bfseries\LARGE{
    \centering
    \centerline{What can we tell about contact}

@@

  \block{Barab\'asi-Albert preferential attachment networks}{
    Nodes are added one at a time until there are $N$ total. Each time a node
    is added, $m$ new edges are connected to it. Each new edge is attached to
    an existing node of degree $d$ with probability proportional to
    $d^\alpha$.

    \vspace{1cm}
    \centerline{\includegraphics[width=0.2\textwidth]{pa-example}}
    \vspace{1cm}

    \begin{center}
      \begin{tabular}{cl}
        parameter & meaning \\
        \hline
        $\alpha$ & preferential attachment power \\
        $m$ & number of new edges added for each new vertex \\
        $I$ & number of infected nodes when epidemic is stopped \\
        $N$ & total number nodes in the network \\
        \hline
      \end{tabular}
    \end{center}
    \node at (1, 10) {low $\alpha$};
    \node at (14, 10) {high $\alpha$};
  }

@@

  \block{Varying $\alpha$ and $I$ affects tree shape, but not $m$ and $N$}{
    \centerline{\includegraphics[width=0.18\textwidth]{kernel-kpca}}

@@

    \vspace{0.5cm}
    \captionof{table}{
    Three networks/trees were simulated under each parameter combination.
    Kernel-ABC was used to re-estimate the parameters.
    }
  }
  \block{Accurate estimates for $\alpha$, $I$; not $m$, $N$}{
    \centerline{\includegraphics[width=0.16\textwidth]{abc-point-estimate-m2}}
    Dotted lines are true values. $\alpha$ and $I$, which had the most impact
    on tree shape, were possible to estimate accurately. Posterior
    distributions of $m$ and $N$ heavily resemble the priors, indicating
    little information about these parameters in the trees.
  }
  \block{Narrow dispersion of $\alpha$, $I$ compared to $m$, $N$}{
    \centerline{\includegraphics[width=0.16\textwidth]{abc-posterior-example}}
  }

@@

  \block{Real data: phylogenetic and geographic clusters}{
    \centering
    \input{\tablepath/realdata}
    \captionof{table}{
      Characteristics of HIV datasets analysed with kernel-ABC. Abbreviations:
      MSM, men who have sex with men; IDU, injection drug users.
    }
  }

@@

  \block{Parameter heterogeneity among real datasets}{
    \vspace{1cm}
    \centerline{\includegraphics[width=0.25\textwidth]{realdata-hpd}}
    \vspace{1cm}
  }
\end{columns}

@@

      Due to the simple nature of the Barab\'asi-Albert model, it is likely
      misspecified for the real data we analyzed, and therefore caution must be
      exercised in interpreting the estimated values. However, the possibility
      to investigate more realistic models in the future makes our approach a
      useful tool for phylodynamic research on contact networks.
    \end{multicols}
  }
  \block{}{
    \begin{minipage}{0.55\linewidth}
      \vspace{1cm}
      \includegraphics[width=3in]{logos/btp}
      \includegraphics[width=3in]{logos/cfe}
      \includegraphics[width=1.5in]{logos/cihr}
      \includegraphics[width=3in]{logos/msfhr}
      \includegraphics[width=2in]{logos/phc}
      \includegraphics[width=0.9in]{logos/ubc}
      \vspace{0.5cm}
    \end{minipage}
    \begin{adjustbox}{valign=t}
      \begin{minipage}[t]{0.45\linewidth}
        \small
        This work was supported by a grant from the Canadian Institutes for
        Health Research (CIHR HOP-111406 to AFYP) and a scholarship from the 
        Canadian Institutes for Health Research  Strategic Training Program in
        Bioinformatics (to RMM). AFYP is the recipient of a Scholar Award from
        the MSFHR/St. Paul’s Hospital Foundation - Providence Health Care
        Research Institute Career Investigator program, and a CIHR New
        Investigator Award.
      \end{minipage}
    \end{adjustbox}
  }

  \column{0.35}
  \block{References} {
    \renewcommand*{\bibfont}{\footnotesize}
    \printbibliography[heading=none]
    \small
    \includegraphics[height=1cm]{logos/westgrid} Analyses were run in the
    Westgrid high performance computing environment.
  }

\end{columns}

>>>>

\addbibresource{papers.bib}
\setlength{\bibhang}{0pt}
\DeclareBibliographyCategory{ignore}
\addtocategory{ignore}{zetterberg2004two}
\addtocategory{ignore}{niculescu2015recent}
\addtocategory{ignore}{novitsky2013phylogenetic}
\addtocategory{ignore}{novitsky2014impact}
\addtocategory{ignore}{mccormack2002early}
\addtocategory{ignore}{grabowski2014role}
\addtocategory{ignore}{wang2015targeting}
\addtocategory{ignore}{kao2011surveillance}
\addtocategory{ignore}{little2014using}
\addtocategory{ignore}{li2015hiv}
\addtocategory{ignore}{cuevas2009hiv}

\tikzposterlatexaffectionproofoff
\settitle{ \vbox{ \centering \color{titlefgcolor}
{\fontsize{2.5cm}{2cm}\selectfont \@title}
\\ --- \huge \@author~--- \\ \@institute } }

@@

% hacky things
\node [text width=6in] at ($ (current page.west) + (-0.42\paperwidth, -1.5in) $)
  { \LARGE ISMB \\ July 8-12, 2016 \\ Orlando, USA};
\node [text width=6in, align=right] at ($ (current page.west) + (0.42\paperwidth, -1.5in) $)
  { \LARGE rmccloskey@cfenet.ubc.ca \\ (604) 558-8865 };

\begin{columns}
  \column{0.25}
  \block{Contact networks shape viral transmission trees}{
    \centerline{\includegraphics[width=0.22\textwidth]{contactnet}}
      Network structure can change the speed and pattern of epidemic spread,
      potentially informing public health interventions.
  }
  \block{}{\vspace{1cm}\color{blocktitlefgcolor}\bfseries\LARGE{
    \centering
    \centerline{What can we tell about contact}

@@

  \block{Barab\'asi-Albert preferential attachment networks}{
    Nodes are added one at a time until there are $N$ total. Each time a node
    is added, $m$ new edges are connected to it. Each new edge is attached to
    an existing node of degree $d$ with probability proportional to
    $d^\alpha + 1$.

    %\node at (0, 0) {sub-linear $\alpha$};
    %\node at (14, 6.5) {linear $\alpha$};
    %\node at (23, 7.5) {super-linear $\alpha$};

    \begin{center}
      \begin{tikzpicture}
        \node (a) {\includegraphics[width=0.22\textwidth]{pa-example}};
        \node at (a.south) [anchor=north] {sub-linear $\alpha$ $\qquad\qquad\qquad$ linear $\alpha$ $\qquad\qquad\qquad$ super-linear $\alpha$};
      \end{tikzpicture}
    \end{center}

    \begin{center}
      \begin{tabular}{cl}
        parameter & meaning \\
        \hline
        $\alpha$ & preferential attachment power \\
        $m$ & number of new edges added for each new vertex \\
        $I$ & number of infected nodes when epidemic is stopped \\
        $N$ & total number nodes in the network \\
        \hline
      \end{tabular}
    \end{center}
  }

@@

  \block{Varying $\alpha$ and $I$ affects tree shape, but not $m$ and $N$}{
    \centerline{\includegraphics[width=0.16\textwidth]{kernel-kpca}}

@@

    \vspace{0.5cm}
    \captionof{table}{
    Three networks/trees were simulated under each parameter combination.
    Kernel-ABC was used to re-estimate the parameters.
    }
  }
  \block{Accurate estimates for $\alpha$, $I$; not $m$, $N$}{
    \centerline{\includegraphics[width=0.16\textwidth]{abc-point-estimate-m2}}
    Dotted lines are true values. $\alpha$ and $I$, which had the most impact
    on tree shape, were possible to estimate accurately. Posterior
    distributions of $m$ and $N$ heavily resemble the priors, indicating
    little information about these parameters in the trees.
  }
  \block{Narrow dispersion of $\alpha$, $I$ compared to $m$, $N$}{
    \centerline{\includegraphics[width=0.15\textwidth]{abc-posterior-example}}
  }

@@

  \block{Real data: phylogenetic and geographic clusters}{
    \centering
    \normalsize
    \input{\tablepath/realdata}
    \captionof{table}{
      Characteristics of HIV datasets analysed with kernel-ABC. Abbreviations:
      MSM, men who have sex with men; IDU, injection drug users.
    }
  }

@@

  \block{Stronger preferential attachment in IDU networks}{
    \includegraphics[trim=0 3.5in 3.3in 0, clip, width=0.12\textwidth]{realdata-hpd}
    \includegraphics[trim=3.4in 1.5in 0 2.0in, clip, width=0.12\textwidth]{realdata-hpd}
    \vspace{1cm}
  }
\end{columns}

@@

      Due to the simple nature of the Barab\'asi-Albert model, it is likely
      misspecified for the real data we analyzed, and therefore caution must be
      exercised in interpreting the estimated values. However, the possibility
      to investigate more realistic models in the future makes our approach a
      useful tool for phylodynamic research on contact networks.
    \end{multicols}
  }
  \column{0.35}
  \block{References} {
    \renewcommand*{\bibfont}{\footnotesize}
    \printbibliography[notcategory=ignore, heading=none]
    \small
    \includegraphics[height=1cm]{logos/westgrid} Analyses were run in the
    Westgrid high performance computing environment.
  }
\end{columns}
\block{}{
  \begin{minipage}{0.6\linewidth}
    \vspace{1cm}
    \includegraphics[width=4in]{logos/btp}
    \quad
    \includegraphics[width=4in]{logos/cfe}
    \quad
    \includegraphics[width=2in]{logos/cihr}
    \quad
    \includegraphics[width=3in]{logos/msfhr}
    \quad
    \includegraphics[width=3in]{logos/phc}
    \quad
    \includegraphics[width=1in]{logos/ubc}
    \quad
    \includegraphics[width=1.8in]{logos/genomecanada}
    \quad
    \includegraphics[width=2.2in]{logos/genomebc}
    \quad
    \includegraphics[width=1.8in]{logos/genomequebec}
    \vspace{0.5cm}
  \end{minipage}
  \begin{adjustbox}{valign=t}
    \begin{minipage}[t]{0.4\linewidth}
      \small
      This work was supported by a grant from the Canadian Institutes for
      Health Research (CIHR HOP-111406 to AFYP) and a scholarship from the 
      Canadian Institutes for Health Research  Strategic Training Program in
      Bioinformatics (to RMM). AFYP is the recipient of a Scholar Award from
      the MSFHR/St. Paul’s Hospital Foundation - Providence Health Care
      Research Institute Career Investigator program, and a CIHR New
      Investigator Award.
    \end{minipage}
  \end{adjustbox}
}

### 2016-07-01 doc/paper/changes.tex
Progress on paper changes

Thank you for the opportunity to revise our manuscript ``Reconstructing contact
network parameters from viral phylogenies''.

While our submission was pending, we made some additions and improvements to
the work that we would like you and the reviewers to consider. It was pointed
out to us by a colleague that the posterior mean is a more conventionally used
estimator than the maximum \textit{a posteriori} (MAP) value. Therefore, we
have replaced the MAP point estimates by posterior means. Qualitatively, the
results are not much different, except that it is more obvious that $m$ and $N$
are not identifiable with this method. We have replaced some ad hoc statistical
tests in the analysis of the simulation results with a $p$-value corrected
generalized linear model, and rewritten the relevant section of the results
accordingly. For clarity, the real HIV datasets are now referred to as their
risk group and location in the text, rather than by their author (eg.
MSM/Beijing instead of Wang et al.). We have found an analysis of the
Barab\'asi-Albert model in the physics literature which demonstrates that the
degree distribution is only a power law when $\alpha = 1$. We acknowledge this
but do not believe it detracts from the validity of our results, especially in
light of a paper by de Blasio et al. (2007) which found sub-linear preferential
attachment through a population-level survey.

We did some additional literature searching and found five more published HIV
datasets that seemed to be appropriate for our method. The highest $\alpha$
values were associated with IDU networks, coroborating the assertion of
Dombrowski et al. (2013) that IDU networks exhibit the scale-free property more
strongly than sexual networks do. Three of these new datasets had sequenced two
HIV genes, which we analysed separately. We found that estimates of $\alpha$
were very robust to the choice of gene; $I$ was less robust, with \textit{env}
genes tending to lead to higher estimated values.

Our responses to each of the reviewers' comments are in line below. We were
asked by the Editor in Chief to consider how to disambiguate ABC approximation
error from a truly noisy posterior, which this is addressed under the first
point brought up by Reviewer 1.

@@

We are grateful that the reviewer finds our work to be of some interest, and we
acknowledge that the identifiability of the BA parameters from tree shapes is
somewhat limited. TODO

We have included several new analyses that attempt to disambiguate true
features of the posterior distribution from artefacts of a poor ABC
approximation. First, we used ABC to estimate marginal posterior distributions
when some combinations of parameters were held fixed to known values.
Estimation error which is removed during marginal estimation is likely to be
due to confounding between model parameters; error which remains may be due to
either poor resolution or truely diffuse posteriors. TODO

@@

We apologise for the misunderstanding. Our choice of words was poor -- TODO

We have redone this analysis using both SVMs (classifiers) and SVRs
(regressions). Figure 1 has been expanded to show both sets of results --
accuracy for the SVMs and $R^2$ for the SVRs. The results are qualitatively
very similar.

@@

We thank the reviewer for this helpful suggestion. We individually fixed each
combination of parameters and performed ABC inference on the remaining free
parameters. The inference of $I$ was dramatically improved when $N$ was fixed.
Fixing each of the parameters contributed slightly to the estimate of $\alpha$,
but none as dramatically. However, the posterior mean estimate of $m$ was
totally unaffected by fixing the other parameters. This indicates that our
inability to estimate $m$ is simply due to lack of identifiability, rather than
to parameter correlations.

As the reviewer suggested, we have also included a set of two-dimensional
posterior distributions in the text (Figure TODO). The correlation between $N$
and $I$ demonstrated in the marginal analysis is clearly observable, but there
are no obvious correlations among the other parameters.

@@

We agree with this assessment of our visual presentation of the results. We
have reduced the number of posterior plots shown to one in the text and two in
the supplemental materials. TODO

@@

@@

Although they are very approximate methods, our experience has been that using
approximate maximum likelihood phylogeny reconstruction with root-to-tip
regression does not result in large errors in phylodynamic inference (Poon et
al. 2015). We reanalysed the datasets with the highest and lowest estimated
$\alpha$ (Zetterberg et al. 2004 and Cuevas et al. 2009) using a BEAST MCC tree 
from a run with simple models of evolution and population size. The results
were TODO

@@

TODO dunno man

@@

This statement has been removed in our updated version. When we calculated
posterior means rather than modes, as is more conventional, we found that
nearly all of the estimates were very near to the middle of the range. This is
consistent with our observed lack of signal for $m$ in phylogenetic data.

@@

Since several of the datasets had the majority of their posterior mass on $m =
1$, it seemed that this choice of prior was more reasonable, and we therefore
focused our discussion on those results.

@@

We agree that the sloped lines were misleading and have replated them with
horizontal line segments. TODO

@@

@@

As mentioned above, we have focused our discussion on $m = 1$ due to the
several datasets for which $m = 1$ contained most of the posterior mass.

@@

This is a valid point, and in fact drawing $m$ from a distribution is an
approach we considered when we were performing this work. However, since this
is our first attempt to fit network models, we thought it best to stick with
a simple, well-known model rather than defining our own parameters. (TODO: We
have added to the discussion the point that this binary choice is sub-optimal
and suggested this enhancement for future work.)

>>>>

Thank you for the opportunity to revise our manuscript ``Reconstructing contact
network parameters from viral phylogenies''. While our submission was pending,
we made some additions and improvements to the work that we would like you and
the reviewers to consider.

\begin{itemize}

  \item It was pointed out to us by a colleague that the posterior mean is a
    more conventionally used Bayesian estimator than the maximum \textit{a
    posteriori} (MAP) value. Therefore, we have replaced the MAP point
    estimates by posterior means. Qualitatively, the results are not much
    different, except that it is more obvious that $m$ and $N$ are not
    identifiable with this method. 
  \item We have replaced some ad hoc statistical tests in the analysis of the
    simulation results with a $p$-value corrected generalized linear model, and
    rewritten the relevant section of the results accordingly.
  \item We have found an analysis of the Barab\'asi-Albert model in the physics
    literature (Krapivsky et al. 2000) which demonstrates that the degree
    distribution is only a power law when $\alpha = 1$. We acknowledge this but
    do not believe it detracts from the validity of our results, especially in
    light of a paper by de Blasio et al. (2007) which found sub-linear
    preferential attachment through a population-level survey. We have added to
    the supplemental materials a series of power law fits to the degree
    distributions of BA networks with $\alpha \neq 1$ (Figure TODO), which
    shows that, although the power law is cleary an imperfect fit, the slope
    is still reasonably representative of the true distribution.
  \item We did some additional literature searching and found five more
    published HIV datasets that seemed to be appropriate for our method. For
    clarity, the real HIV datasets are now referred to by risk group and
    geographic location, rather than by author (eg. MSM/Beijing instead of Wang
    et al.). The highest $\alpha$ values were associated with IDU networks,
    coroborating the assertion of Dombrowski et al. (2013) that IDU networks
    exhibit the scale-free property more strongly than sexual networks do. 
  \item Three of these new datasets had sequenced two HIV genes, which we
    analysed separately. We found that estimates of $\alpha$ were very robust
    to the choice of gene; $I$ was less robust, with \textit{env} genes tending
    to lead to higher estimated values.
  \item Figure 5 (formerly Figure 4) now shows 50\% HPD intervals (similar to
    interquartile ranges) in addition to 95\% HPD intervals.
  \item We discovered that our use of the term ``kernel-ABC'' to refer to ABC 
    with a kernel for the distance function is in conflict with another usage,
    namely an expression of Bayes' rule in terms of kernel means (Fukumizu et
    al. ``Kernel Bayes' rule.'' 2011). We therefore simply use the term ``ABC''
    to refer to our method.
  \item The discussion has been divided into subsections to make it easier to
    follow.
\end{itemize}

Our responses to each of the reviewers' comments are in line below. We were
asked by the Editor in Chief to consider how to disambiguate ABC approximation
error from a truly noisy posterior, which is addressed under the first point
brought up by Reviewer 1.

@@

We are grateful that the reviewer finds our work to be of some interest, and we
acknowledge that our ability to precisely resolve numerical values of the BA
parameters is limited. We believe that our simulation results show that some
network parameters (specifically $\alpha$ in our case) can be at least roughly
estimated from the information contained in tree shapes.

We have included several new analyses that attempt to disambiguate true
features of the posterior distribution from artefacts of a poor ABC
approximation. First, we used ABC to estimate marginal posterior distributions
when some combinations of parameters were held fixed to known values.
Estimation error which is removed during marginal estimation is likely to be
due to confounding between model parameters; error which remains may be due to
either poor resolution or truely diffuse posteriors. The accuracy of the
estimates was improved about 50\% in marginal estimation.

@@

We apologise for this misunderstanding due to our poor choice of words. An SVR
is in fact a regressor, not a classifier, so the reported $R^2$ were of true
values against predictions. However, given that the point of this experiment
was to demonstrate identifiability by categorizing tree shapes into
predetermined values, we redid the analysis using SVMs (which are true
classifiers) instead of SVRs and linear regression. We now report the accuracy
of the categorical classification, and figures 1 and S3-S6 have been revised
accordingly. Some additional variation among meta-parameters and epidemic
scenarios is observed, but the overall results are similar and the best choice
of meta-parameters is the same.

@@

We thank the reviewer for this helpful suggestion, which we addressed by
marginal estimation as outlined under the first comment. The inference of $I$
was dramatically improved when $N$ was fixed. Fixing each of the parameters
contributed slightly to the estimate of $\alpha$, but none as dramatically.
However, the posterior mean estimate of $m$ was totally unaffected by fixing
the other parameters. This indicates that our inability to estimate $m$ is
simply due to lack of identifiability, rather than to parameter correlations.

As suggested, we have also included a set of two-dimensional posterior
distributions in the text (Figure 4). The correlation between $N$ and $I$
demonstrated in the marginal analysis is clearly observable, but there are no
obvious correlations among the other parameters.

@@

We agree with this assessment of our visual presentation of the results. We
have reduced the number of posterior plots shown to one in the text and two in
the supplemental materials. Figure 2, which formerly represented each
simulation by an individual point, has been replaced by a box plot showing the
$\alpha$ and $I$ estimates stratified by each of the other parameters. A
similar boxplot for $m$ and $N$, which were not identifiable with ABC, has been
added to the supplemental materials.

@@

We have changed the phrase to ``effective viral population size.''

@@

Although they are very approximate methods, our experience has been that using
approximate maximum likelihood phylogeny reconstruction with root-to-tip
regression does not result in large errors in phylodynamic inference (Poon
2015). We reanalysed the datasets with the highest and lowest estimated
$\alpha$ (Zetterberg et al. 2004 and Cuevas et al. 2009) using a BEAST MCC tree
from a run with simple models of evolution and population size. The results
were TODO

With respect to the suggestion to analyse bootstrap replicates, we believe that
the three new datasets containing both \textit{gag} and \textit{env} data fill
the need for within-dataset replication.

@@

We think the reviewer is referring to Figure S3, which shows the
cross-validation accuracy of the SVM classifier for $\alpha$ under several
values of the tree kernel meta-parameters $\lambda$ and $\sigma$. However,
higher $\sigma$ values ($x$-axis) lead to better estimates, not worse, and for
most meta-parameter combinations the estimates get worse, not better, on
smaller datasets.

In any case, we can offer a few comments on this figure. When $\sigma = 0$,
subset trees only match when their branch lengths are identical. As $\sigma \to
\infty$, branch lengths are not taken into account at all, and matches are
based on topology alone. Thus, it seems that topology is more important for
classifying $\alpha$ than branch lengths are, which is consistent with our
observation that $\alpha$ strongly affects tree balance. The decay factor
$\lambda$ is intended to penalize very large subset tree matches which can
dominate the kernel score (see Poon et al. 2013). This ``large match'' problem
becomes worse as the trees become larger. For the largest trees we considered, 
it seems that $\lambda = 0.4$ was not a strict enough penalty, leading to a
decrease in classification accuracy.

Part of the new text introducing the classification experiments now contains a
short description of the two meta-parameters. In addition, a brief comment
on the effects of $\lambda$ and $\sigma$ on the classifiers has been added to
the first paragraph of the results section.

@@

The reviewer's interpretation is correct, but this statement has been removed
in our updated version. When we calculated posterior means rather than modes,
as is more conventional, we found that nearly all of the estimates were very
near to the middle of the range. This is consistent with our observed lack of
signal for $m$ in phylogenetic data.

@@

Since several of the datasets had the majority of their posterior mass on $m =
1$, it seemed that this choice of prior was more reasonable, and we therefore
focused our discussion on those results. The alternative results are presented
in the last paragraph of the discussion.

@@

As per Reviewer 1's suggestion we have replaced Figure 2 with a boxplot showing
posterior means stratified by the true parameter values. We agree that the
sloped lines were misleading and have replaced them with horizontal line
segments.

@@

This issue was also addressed by performing marginal estimation. If the
accurate estimates of $I$ were solely due to the prior, they would have gotten
worse, not better, when $N$ was fixed and the prior on $I$ was truly uniform.
We make this point in the discussion: ``when $I$ was estimated marginally with
fixed $N$, the accuarcy of the estimate improved even though there was no
longer any extra prior mass on low $I$ values.''

@@

We have focused our discussion on $m = 1$ due to the several datasets for which
$m = 1$ contained most of the posterior mass.

@@

This is a valid point, and in fact drawing $m$ from a distribution is an
approach we considered when we were performing this work. However, since this
is our first attempt to fit network models, we thought it best to stick with
a simple, well-known model rather than defining our own parameters. We did
perform a small experiment allowing heterogeneity among nodes, but in $\alpha$
rather than in $m$, and recovered the average of the two $\alpha$ values.

(TODO: We
have added to the discussion the point that this binary choice is sub-optimal
and suggested this enhancement for future work.)
